Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-14 csf-2017/paper.tex
Two minor modifications.
Stack management added

\textbf{Invoking the adversary} Slightly more complex is the case where we
invoke the adversary. As above, we clear all the registers, except those that
contain arguments the adversary is intended to have access to. We leave a copy
of the stack pointer in the appropriate register, but only after we have used
the $\subseg{}{}{}$ to shrink its authority to just the part of the stack that
we are not using. In one of the registers, we also provide a return pointer,
which we will say more about below.

@@

\textbf{Reusable macro instructions} With the high-level approach in mind, we
define the following macro instructions: \texttt{fetch $r$ $\var{name}$} fetches
the capability related to $\var{name}$ from the linking table and stores it in
register $r$. \texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack pointer in register $r_\stk$.
\texttt{prepstk $r$} is used when a callback is invoked by the adversary and
prepares the received stack pointer by checking that it has permission $\rwlx$
and making it conform to our stack discipline. \texttt{scall
  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)} Jumps to the
capability in register $r$ in the manner described above. That is, it pushes local state (the
contents of registers $\overline{r_{\var{priv}}}$), stack pointer and return
pointer to the stack, sets up the necessary on stack return code and creates a
return pointer, restricts stack pointer, clears the unused part of the stack,
clears the necessary registers and jumps to $r$. Upon return, the private state
is restored. \texttt{mclear $r$} clears all the memory the capability in
register $r$ has authority over. \texttt{rclear $\var{regSet}$} clears all the
registers in $\var{regSet}$ \texttt{reqglob $r$} checks whether the word in
register $r$ is a global capability. \texttt{crtcls $\overline{(x_i,r_i)}$ $r$}
allocates a closure pair where the capability in register $r$ is used to point
to the program and a new environment is allocated (using malloc) where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an implicit fetch
happens when an instruction refers to $x_i$.

>>>>

\textbf{Invoking the adversary} Slightly more complex is the case where we
invoke the adversary. As above, we clear all the registers, except those that
contain arguments the adversary is intended to have access to. We leave a copy
of the stack pointer in $r_\stk$, but only after we have used
the $\subseg{}{}{}$ to shrink its authority to just the part of the stack that
we are not using. In one of the registers, we also provide a return pointer,
which we will say more about below.

@@

\textbf{Stack management discipline}
The precautions the stack discipline must take have now been introduced and motivated. Summarized, the stack discipline is:
\begin{description}
\item[At program startup] a local $\rwlx$-capability (the stack pointer) resides in register $r_\stk$. The system does not hand out global write-local capabilities.
\item[Before returning to the adversary] clear the registers (with words we do not want to pass to the adversary) and erase any part of the stack we have used.
\item[Before invoking the adversary] push an activation record to the stack, create a local $\entry$-capability for the restore instructions of the activation record (the return pointer) and leave it in register $r_0$, leave a copy of the stack capability restricted to the unused part in $r_\stk$, erase the part of the stack we release control over, and clear the non-argument registers.
\item[Before invoking an adversary call] make sure it is a global capability.
\item[When having a call back invoked by the adversary] make sure the alleged stack pointer has permission $\rwlx$.
\end{description}

\textbf{Reusable macro instructions} 
We define a number of reusable macros. Some of them capture the stack
management discipline and others make the examples in
Section~\ref{sec:examples} readable. The macros are:
\texttt{fetch $r$ $\var{name}$} fetches the capability related to
$\var{name}$ from the linking table and stores it in register
$r$. \texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack pointer in register
$r_\stk$.  \texttt{prepstk $r$} is used when a callback is invoked by
the adversary and prepares the received stack pointer by checking that
it has permission $\rwlx$ and making it conform to our stack
discipline. \texttt{scall
  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)} Jumps
to the capability in register $r$ in the manner described above. That
is, it pushes local state (the contents of registers
$\overline{r_{\var{priv}}}$), stack pointer and return pointer to the
stack, sets up the necessary on stack return code and creates a return
pointer, restricts the stack pointer, clears the unused part of the
stack, clears the necessary registers and jumps to $r$. Upon return,
the private state is restored. \texttt{mclear $r$} clears all the
memory the capability in register $r$ has authority
over. \texttt{rclear $\var{regSet}$} clears all the registers in
$\var{regSet}$. \texttt{reqglob $r$} checks whether the word in
register $r$ is a global capability. \texttt{crtcls
  $\overline{(x_i,r_i)}$ $r$} allocates a closure pair where the
capability in register $r$ is used to point to the program and a new
environment is allocated (using malloc) where the contents of
$\overline{r_i}$ is stored. In the program referred to by $r$, an
implicit fetch happens when an instruction refers to $x_i$.
